---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(tsibble)
library(lubridate)
```

```{r}
regional_domestic_tourism_clean
```

```{r}
scottish_accomodation_occupancy_clean 
```

```{r}
tourism_day_visits_activities_clean
```


```{r}
tourism_day_visits_demmographics_clean
```


```{r}
tourism_day_visits_location_clean
```


```{r}
tourism_day_visits_transport_clean
```





Q8 _How have general tourism rates changed over time?_
 _OCCUPANCY_
Change over the years, different size of the occupancy by its type
```{r}
#To avoid problems because there are too many points: group_by and summarise
scottish_accomodation_occupancy_clean %>% 
  group_by(accommodation_type_and_occupancy, year) %>% 
  summarise( average_occupancy = mean(value)) %>% 
ggplot(aes( x = year, y = average_occupancy, colour = accommodation_type_and_occupancy))+
  geom_line() +
  facet_wrap(~accommodation_type_and_occupancy, scales = 'free_y')+
labs(
    title = "GB Occupancy in Scotland between 2011 -2019",
    x = "\nYear",
    y = "Average occupancy\n") +
    scale_colour_brewer(guide = "none", palette = "Set2")+
   scale_x_continuous(breaks = 2011:2019)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r}
scottish_accomodation_occupancy_clean %>% 
  select(year, value,accommodation_type_and_occupancy) %>% 
  ggplot(aes( x = year, y = value,group = accommodation_type_and_occupancy, colour =        accommodation_type_and_occupancy))+
  geom_line()
```

```{r}
scottish_accomodation_occupancy_clean %>% 
  ggplot(aes( x = accommodation_type_and_occupancy))+
  geom_bar(fill = "light blue", colour = "red")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

 _VISITS/LOCATIONS_
In general we see there is a tendency to a slowly fall in the visits for all GB to Scotland. This fact is more clear in 'urban' areas or where it could be more visitors.

```{r}
tourism_day_visits_location_clean %>% 
  filter(breakdown_of_domestic_tourism =='Visits') %>% 
  group_by(type_of_location_visited, year) %>% 
  summarise( average_visits = mean(value)) %>% 
ggplot(aes( x = year, y = average_visits, colour = type_of_location_visited))+
  geom_line() +
  facet_wrap(~type_of_location_visited, scales = 'free_y')+
labs(
    title = "GB Visits in Scotland between 2011 -2019",
    x = "\nYear",
    y = "Average visits\n") +
    scale_colour_brewer(guide = "none", palette = "Set2")+
   scale_x_continuous(breaks = 2011:2019)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


_DEMOGRAPHICS_
By age, each year is different, for 2019 the data show that mostly all the age groups falland the only two that grow significantly , 65 or older and 35-44 years old , are under the mark of their beat year that was 2016.

```{r}
tourism_day_visits_demmographics_clean %>% 
  select(breakdown_of_domestic_tourism, age, value,year) %>% 
  filter(age != 'All') %>% 
  filter(breakdown_of_domestic_tourism == 'Visits') %>% 
  ggplot(aes( x = year, y = value, colour = age))+
  geom_line()+
  labs(
    title = "GB Visitors Age in Scotland between 2011 -2019",
    x = "\nYear",
    y = "Average Thousand visits\n") +
   scale_colour_brewer( palette = "Set2")+
   scale_x_continuous(breaks = 2013:2019)
```

_TRANSPORT_

```{r}
tourism_day_visits_transport_clean %>% 
  filter(breakdown_of_domestic_tourism == 'Visits')
```


```{r}
tourism_day_visits_transport_clean %>% 
  select(method_of_travel,breakdown_of_domestic_tourism, value,year) %>% 
  filter(method_of_travel != 'All') %>% 
  filter(breakdown_of_domestic_tourism == 'Visits') %>% 
  ggplot(aes( x = year, y = value, colour = method_of_travel))+
  geom_line()+
  labs(
    title = "GB Visitors Transport in Scotland between 2011 -2019",
    x = "\nYear",
    y = "millions visits\n") +
   scale_x_continuous(breaks = 2013:2019)
```


```{r}
tourism_day_visits_transport_clean %>% 
  select(method_of_travel,breakdown_of_domestic_tourism, value,year) %>% 
  filter(method_of_travel != 'All') %>% 
  filter(breakdown_of_domestic_tourism == 'Visits') %>% 
  ggplot(aes( x = year, y = value, colour = method_of_travel))+
  geom_line()+
   facet_wrap(~method_of_travel, scales = 'free_y')+
  labs(
    title = "GB Visitors Transport in Scotland between 2011 -2019",
    x = "\nYear",
    y = "millions visits\n") +
   scale_x_continuous(breaks = 2013:2019)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


```{r}
tourism_day_visits_transport_clean %>% 
  select(method_of_travel,breakdown_of_domestic_tourism, value,year) %>% 
  filter(method_of_travel != 'All') %>% 
  filter(breakdown_of_domestic_tourism == 'Expenditure') %>% 
  ggplot(aes( x = year, y = value, colour = method_of_travel))+
  geom_line()+
   facet_wrap(~method_of_travel, scales = 'free_y')+
  labs(
    title = "GB Visitors Transport Expenditure in Scotland between 2011 -2019",
    x = "\nYear",
    y = "millions Pounds\n") +
  # scale_colour_brewer(guide = "none", palette = "Set2")+
   scale_x_continuous(breaks = 2013:2019)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


```{r}
tourism_day_visits_transport_clean %>% 
  select(method_of_travel,breakdown_of_domestic_tourism, value,year) %>% 
  filter(method_of_travel != 'All') %>% 
  filter(breakdown_of_domestic_tourism == 'Expenditure') %>% 
  ggplot(aes( x = year, y = value, fill = method_of_travel))+
  geom_col()+
   #facet_wrap(~method_of_travel, scales = 'free_y')+
  labs(
    title = "GB Visitors Transport Expenditure in Scotland between 2011 -2019",
    x = "\nYear",
    y = "millions Pounds\n") +
   #scale_colour_brewer(guide = "none", palette = "Set2")+
   scale_x_continuous(breaks = 2013:2019)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
Q9

```{r}
predict_spend <- tourism_day_visits_activities_clean
predict_spend
```


My year is not a date is number Should I change to date?

```{r}
predict_spend %>% 
  select(year, breakdown_of_domestic_tourism,tourism_activity,value = value) %>% 
  filter(breakdown_of_domestic_tourism == 'Expenditure') %>% 
  group_by(year,tourism_activity) %>% 
  as_tsibble(index = year )
```

```{r}
predict_spend %>% 
  mutate(year = year(year))
```
















_Extension_
Decission Tree Age-Expenditure

```{r}

library(rpart)
library(rpart.plot)

```
```{r}
tourism_day_visits_demmographics_clean
```
```{r}
demmographics_age_expenditure <- tourism_day_visits_demmographics_clean %>% 
  select(year, value, breakdown_of_domestic_tourism,age) %>% 
  filter(age != 'All') %>% 
  filter(breakdown_of_domestic_tourism == 'Expenditure') %>% 
  group_by(year)
```


 # Train/test split
 
```{r}
n_demmographics_expenditure <- nrow(demmographics_age_expenditure)


test_index_demmographics <-  sample(1 :n_demmographics_expenditure, size = n_demmographics_expenditure * 0.2)

demmographics_expenditure_test <-  slice(demmographics_age_expenditure,test_index_demmographics)

demmographic_expenditure_train <-  slice(demmographics_age_expenditure, - test_index_demmographics)

```

```{r}
decission_age_expenditure <- rpart(formula = age~.,
                                   data = demmographic_expenditure_train ,
                                   method = 'class')


rpart.plot(decission_age_expenditure, yesno = 2,
           fallen.leaves = TRUE,
           faclen = 6,
           digits = 4)

```











