







---
title: "Visit Scotland"
subtitle: "A glimpse"
author: "Juan Ignacio De Vicente Ojeda"
institute: " Tilting at Windmills "
date: "Today: `r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false

---

background-image: url(https://upload.wikimedia.org/wikipedia/commons/b/be/Sharingan_triple.svg)

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(tidyverse)
library(tsibble)
regional_domestic_tourism_clean  <- read_csv("clean_data/regional_domestic_tourism_clean.csv")
scottish_accomodation_occupancy_clean <- read_csv("clean_data/scottish_accomodation_occupancy_clean.csv")
tourism_day_visits_activities_clean <- read_csv("clean_data/tourism_day_visits_activities_clean.csv")
tourism_day_visits_demmographics_clean <- read_csv("clean_data/tourism_day_visits_demmographics_clean.csv")
tourism_day_visits_location_clean <- read_csv("clean_data/tourism_day_visits_location_clean.csv")
tourism_day_visits_transport_clean <- read_csv("clean_data/tourism_day_visits_transport_clean.csv")
visit_sites_activity <-  read_csv("clean_data/visit_sites_activity.csv")
# predict_spend <- tourism_day_visits_activities_clean
# predict_spend <- predict_spend %>% 
#   select(year, breakdown_of_domestic_tourism,tourism_activity,value = value) %>% 
#   filter(breakdown_of_domestic_tourism == 'Expenditure')
#   #tibble::rowid_to_column() %>% 
#   # mutate(year = as.Date(year, '2011-01-01')) %>% 
#   #group_by(year,tourism_activity) %>% 
#   as_tsibble(index = year, key = tourism_activity )
predict_visits <- tourism_day_visits_activities_clean
```

???

Image credit: [Wikimedia Commons](https://commons.wikimedia.org/wiki/File:Sharingan_triple.svg)



---
class: middle, center
# INTRODUCTION


The aim of this presentation is to show a quick glimpse about the domestic tourist sector between the years 2011 and 2019 in Scotland.Specially the value of visits and the expenditure.

In order to conduct this premise, it had been used the the open data offer by 'Visit Scotland' that can be consult in the website of the Scottish Government : 'statistics.gov.scot'

It is understood by domestic tourist  the person which reside in Great Britain



---
# Data Context/ Disclaimer/ Assumptions 

 Before start, it has to be some considerations.
 
- Some of the data used presented the variable 'region of residence', and observations are  'All GB', 'England' and 'Scotland'.  Due the fact that GB means England, Scotland and Wales,it has been used the  'All GB' observation because - in our opinion- should be the most accurate.

- Also one visitor can realize more than one visits. This  fact could lead to a misinterpretation in the total number of visits and visitors.

- In 2019, Visit Scotland in conjunction with Visit England and Visit Wales change the parameters for recording  domestic overnight trips and domestic day trips. It is believed that this new method can produce different interpretations in visits and expenditure. More info. 'INSIGHT DEPARTMENT: GBTS 2021 Methodology and Quality'

- Therefore, the intention is to show a glimpse about how was the tourism  in the country in 2019 and during previous years. Before the introduction of the new method and the disruption caused by the pandemic and the lockdown restrictions during 2020,2021 and the beginning of 2022 plus the current world economic recession.

---


#  Definitions

Tourism day trip is defined as:

- Taking part in one of a pre-defined list of activities (based on international tourism definitions)

- Spending 3 or more hours out of the home on this activity

- The activity is not doing 'very regularly' by the respondent

- The activity not being carried out in the place that the respondent lives or works

- The exception to this was trips to visitor attractions, live sporting events and special public events, which are all counted as tourism day trips even when in the place of residence, provided they fulfill the other three criteria.


---

# Tourism in Scotland
.pull-left[
The first question  it should be ask is 'how much money means the domestic tourist activity for Scotland?'.
This visualization answers the question for the period 2013 to 2019. The highest value was in  2017 which nearly 6 Thousand millions Pounds and the low 2015 with a bit less than 4 Thousand millions Pounds.

]
.pull-right[
```{r ,echo = FALSE}
tourism_day_visits_activities_clean %>%
  select(year,units,value,tourism_activity) %>% 
  filter(tourism_activity == 'All') %>% 
  filter(units == 'million pounds (GBP)') %>% 
  arrange(desc(value)) %>% 
  ggplot(aes( x = year, y = value))+
  geom_col(fill = "light blue", colour = "purple", position = 'dodge')+
  labs(title =  'Value of the GB tourism for Scotland', subtitle = '2013 -2019 Income', x = 'Year', y = 'million pounds' )+
  scale_x_continuous(breaks = 2013:2019)
```
]
---

We  can see which are the Tourism Activity and their income in the total value for the year 2019
"Went out for a meal" was the highest Income. One thing you can do once per week but not 'very regularly'.
```{r,echo = FALSE}
tourism_day_visits_activities_clean %>%
  select(year,units,value,tourism_activity, breakdown_of_domestic_tourism) %>%
  filter(tourism_activity != 'All') %>% 
  filter(breakdown_of_domestic_tourism =='Expenditure') %>% 
  filter(year == 2019) %>% 
  arrange(desc(year)) %>% 
   ggplot(aes( x =reorder(tourism_activity,value), y = value))+
  geom_col(fill = "light blue",
           position = 'dodge')+
  labs(title = 'Scotland Highest income 2019' )+
  xlab('tourism activity' )+
  ylab('million pounds' )+
  coord_flip()
```


---

## However..

The higher number of visits for the same year was...
visit friends or family for leisure (tourism activities?)
```{r ,echo = FALSE}
tourism_day_visits_activities_clean %>% 
  filter(breakdown_of_domestic_tourism != 'Expenditure') %>% 
  filter(year == 2019) %>% 
  filter(tourism_activity != 'All') %>% 
   arrange(desc(value)) %>% 
ggplot(aes( x =reorder(tourism_activity,value), y = value))+
  geom_col(fill = "light blue",
           position = 'dodge')+
  labs(title = 'GB Visits by Tourism Activity in 2019' )+
  xlab('Activity' )+
  ylab('million Visit' )+
  coord_flip()
```

---

Where were the location of these visits?
```{r echo = FALSE}
tourism_day_visits_location_clean %>% 
  select(year, value, type_of_location_visited, breakdown_of_domestic_tourism) %>% 
  filter(breakdown_of_domestic_tourism != 'Expenditure') %>% 
  filter(type_of_location_visited != 'All areas') %>% 
  filter(year == 2019) %>% 
   arrange(desc(value)) %>% 
  ggplot(aes( x =reorder(type_of_location_visited,value), y = value))+
  geom_col(fill = "light blue",
           position = 'dodge')+
  labs(title = 'GB Visits in 2019' )+
  xlab('Location Visited' )+
  ylab('million visit' )+
  coord_flip()
```
---
And the expenditure?

```{r echo = FALSE}
tourism_day_visits_location_clean %>% 
  select(year, value, type_of_location_visited, breakdown_of_domestic_tourism) %>% 
  filter(breakdown_of_domestic_tourism != 'Visits') %>% 
  filter(type_of_location_visited != 'All areas') %>% 
  filter(year == 2019) %>% 
   arrange(desc(value)) %>% 
  ggplot(aes( x =reorder(type_of_location_visited,value), y = value))+
  geom_col(fill = "light blue",
           position = 'dodge')+
  labs(title = 'GB Expenditure in 2019' )+
  xlab('Location Visited' )+
  ylab('million pounds' )+
  coord_flip()
```

---

## But

Even if the City or large town attract the majority of visits and expenditure.From 2017 there is a - relative- decrease in comparison with other locations such as countryside or seaside in the number of visits.
```{r echo = FALSE}
tourism_day_visits_location_clean %>% 
  select(year, value, type_of_location_visited, breakdown_of_domestic_tourism) %>% 
  filter(breakdown_of_domestic_tourism != 'Expenditure') %>% 
  filter(type_of_location_visited != 'All areas') %>% 
   ggplot(aes( x = year, y = value, colour = type_of_location_visited))+
  geom_line() +
  facet_wrap(~type_of_location_visited, scales = 'free_y')+
labs(
    title = "GB Visits in Scotland between 2013 -2019",
    x = "\nyear",
    y = "millions visits\n") +
    scale_colour_brewer(guide = "none", palette = "Set2")+
   scale_x_continuous(breaks = 2013:2019)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

---
## Visitors by age between 2013-2019
It can argue that there is not a clear tendency, each group of age had a preferred year in visit Scotland. With a clear decline from 2017 except for 35-44 and 65 and over.
```{r echo = FALSE}
tourism_day_visits_demmographics_clean %>% 
  select(breakdown_of_domestic_tourism, age, value,year) %>% 
  filter(age != 'All') %>% 
  filter(breakdown_of_domestic_tourism == 'Visits') %>% 
  ggplot(aes( x = year, y = value, colour = age))+
  geom_line()+
  labs(
    title = "GB Visitors Age in Scotland between 2011 -2019",
    x = "\nYear",
    y = "Average Thousand visits\n") +
   scale_colour_brewer( palette = "Set2")+
   scale_x_continuous(breaks = 2013:2019)
```

---
## 
Millions Expenditure by visitors age. More spend people between 25-34 , 35 - 44 and 55-56.

```{r echo = FALSE}
tourism_day_visits_demmographics_clean %>% 
  filter(year == 2019) %>% 
  filter(breakdown_of_domestic_tourism =='Expenditure') %>% 
  filter(age != "All") %>% 
  arrange(desc(value)) %>% 
  ggplot(aes( x = age, y = value))+
  geom_col(fill = "light blue")+
labs(
    title = "GB Expenditure by Age in Scotland 2019",
    x = "\nAge",
    y = "millions Pounds\n") +
    scale_colour_brewer(guide = "none", palette = "Set2")+
  coord_flip()
```

---
## How moved the money in 2019?
 More Female than Male
```{r echo = FALSE}
tourism_day_visits_demmographics_clean %>% 
  filter(year == 2019) %>% 
  filter(breakdown_of_domestic_tourism =='Expenditure') %>% 
  filter(gender != "All") %>% 
  filter(gender != "All" ) %>% 
  arrange(desc(value)) %>% 
  ggplot(aes( x = gender, y = value ))+
  geom_col(fill = "light blue")+
labs(
    title = "GB Expenditure by Gender in Scotland 2019",
    x = "\nAge",
    y = "millions Pounds\n") +
    scale_colour_brewer(guide = "none", palette = "Set2")
```
 
---
## Marital Status in 2019
The level of expenditure is higher in married than not married. Could be the result of to have two salaries.
(Could be an ethical consideration - why/ How the spend the money-)
```{r echo = FALSE}
tourism_day_visits_demmographics_clean %>% 
  filter(year == 2019) %>% 
  filter(breakdown_of_domestic_tourism =='Expenditure') %>% 
  filter(marital_status !="All") %>% 
  arrange(desc(value)) %>% 
  ggplot(aes( x = marital_status, y = value ))+
  geom_col(fill = "light blue")+
labs(
    title = "GB Expenditure by Gender in Scotland 2019",
    x = "\nTaken",
    y = "millions Pounds\n") +
    scale_colour_brewer(guide = "none", palette = "Set2")
```

---
## Childrens in 2019?
No, thanks.
```{r echo =FALSE}
tourism_day_visits_demmographics_clean %>% 
  filter(year == 2019) %>% 
  filter(breakdown_of_domestic_tourism =='Expenditure') %>% 
  filter(children !="All") %>% 
  arrange(desc(value)) %>% 
  ggplot(aes( x = children, y = value ))+
  geom_col(fill = "light blue")+
labs(
    title = "GB Expenditure with Children in Scotland 2019",
    x = "\nChildren",
    y = "millions Pounds\n") +
    scale_colour_brewer(guide = "none", palette = "Set2")
```

---
## Millions Expenditure by Employment Status.
```{r echo = FALSE}
tourism_day_visits_demmographics_clean %>% 
  select(area, year,measurement,units,value,breakdown_of_domestic_tourism,employment_status) %>% 
  filter(year == 2019) %>% 
  filter(breakdown_of_domestic_tourism =='Expenditure') %>% 
  filter(employment_status != "All") %>% 
  arrange(desc(value)) %>% 
  ggplot(aes( x = employment_status, y = value ))+
  geom_col(fill = "light blue")+
labs(
    title = "GB Expenditure By Employment Status in Scotland 2019",
    x = "\n Employment Status",
    y = "millions Pounds\n") +
    scale_colour_brewer(guide = "none", palette = "Set2")+
  theme_update(plot.title = element_text(hjust = 0.5))
```

---
##In conclusion

 The data point out that the profile person that spend more money in Scotland is a young / middle- age female married - maybe recently- without children with employ

---
## Transport means where to go, free to travel....
 
 How travel people that visit Scotland and their expenditure in relation.

Answer : Mostly by car and sometimes by Train

---
## GB Visits by travel method in 2019

```{r echo = FALSE}
 tourism_day_visits_transport_clean %>% 
    filter(year == 2019) %>% 
    filter(breakdown_of_domestic_tourism =='Visits') %>% 
    filter(method_of_travel != 'All') %>% 
    arrange(desc(value)) %>% 
    ggplot(aes(x =reorder(method_of_travel,value), y = value))+
    geom_col(fill = "light blue",
             position = 'dodge')+
    #labs(title = 'GB Visits by travel method in 2019' )+
    xlab('Method of travel' )+
    ylab('million visit' )+
    coord_flip()+
    theme_update(plot.title = element_text(hjust = 1))
```

---
## Expenditure in 2019


```{r echo = FALSE}
tourism_day_visits_transport_clean %>% 
  filter(year == 2019) %>% 
  filter(breakdown_of_domestic_tourism =='Expenditure') %>% 
   filter(method_of_travel != 'All') %>%
  arrange(desc(value)) %>% 
  ggplot(aes(x =reorder(method_of_travel,value), y = value))+
  geom_col(fill = "light blue", #colour = "purple",
           position = 'dodge')+
  labs(title = 'GB Expenses By Travel Method in 2019' )+
  xlab('Method of travel' )+
  ylab('million pounds' )+
  coord_flip()
```
---



- The most used transport is the car
- Only 0.4 million visits were in a caravan or campervan but the value of their expenditure was 24.2 millions of pounds. 
- There are few things interesting, 0.5 million visits arrive by sea (boat/ship/ ferry). Where is cruise is boat a cruise? Ship and ferry can include go to the     Islands? 
- We can conclude that is minimum visits some Islands that is needed a sea transport such  as Mull, Islay, Arran. Others places such as Western Islands , Orkney  or Shetlands have airports. Visit  the Islands imply more nights and more expenses
- In 2019 , airplane transport was around 1.5 million of visits (10th position) but reported 123 millions of pounds ( 7 th position). Planes are more to arrive to any airport and later take a hired vehicle , taxi.... So its a way to arrive to Scotland more than travel around the country.
---

## Where people paying out
Places in relation with the use of car and train as a main transport.
```{r echo = FALSE}
regional_domestic_tourism_clean %>% 
  select( area ,year, value, units,region_of_residence,breakdown_of_domestic_tourism ) %>% 
  filter(year == '2017-2019') %>% 
  filter(region_of_residence == 'All of GB') %>% 
  filter(area != 'Scotland') %>% 
  filter(breakdown_of_domestic_tourism == 'Expenditure') %>% 
  arrange(desc(value)) %>% 
   ggplot(aes(x =reorder(area,value), y = value))+
  geom_col(fill = "light blue",
           position = 'dodge')+
  labs(title = 'GB Expenses By Regions during period 2017- 2019' )+
  xlab('Scottish Region' )+
  ylab('million pounds' )+
  coord_flip()
```
---

## Go to...
It could be deduced that is not only  how to arrive,it is the offer of activities in each location.

```{r echo = FALSE}
regional_domestic_tourism_clean %>% 
  select( area ,year, value, units,region_of_residence,breakdown_of_domestic_tourism ) %>% 
  filter(year == '2017-2019') %>% 
  filter(region_of_residence == 'All of GB') %>% 
  filter(area != 'Scotland') %>% 
  filter(breakdown_of_domestic_tourism == 'Visits') %>% 
  arrange(desc(value)) %>% 
   ggplot(aes(x =reorder(area,value), y = value))+
  geom_col(fill = "light blue",
           position = 'dodge')+
  labs(title ='GB Visits By Regions during period 2017- 2019')+
  xlab('Scottish Region' )+
  ylab('Thousand visits' )+
  coord_flip()
```

---

## Accommodation


-There is - at least- one difference between Room and Bed occupancy. Room means the number of occupants per room but Bed  means the number of occupants in a room per quantity/size bed = 1 single bed and 1 double bed  means 3 max occupants.

 -Hotels difference between  Rooms and Bed occupancy. Rooms for weekday and beds during weekend. 
 
 -The occupancy of a room during weekdays could be related with working travels plus leisure/spare time. In tis case a room can have a double bed occupy by one person.

---

```{r echo = FALSE}
scottish_accomodation_occupancy_clean %>%
  select(area,year,value,accommodation_type_and_occupancy,location, weekday_weekend) %>% 
  filter(year == 2019) %>% 
  filter(location == 'All') %>% 
  filter(weekday_weekend != 'All') %>% 
  group_by(accommodation_type_and_occupancy) %>% 
  arrange(desc(value),accommodation_type_and_occupancy) %>% 
  ggplot(aes(fill= weekday_weekend, y=value, x=accommodation_type_and_occupancy)) + 
    geom_bar(position="dodge", stat="identity")+
 labs(
    title ="Occupancy by Accomodation Type in Scotland  in 2019",
    x = "\n Accomodation Type",
    y = "Percentage Over Total Occupancy\n") +
   coord_flip()+
  theme_update(plot.title = element_text(hjust = 0.5))
```


---


## Predictions 

As it was mentioned before the data covers mostly the period 2013- 2019.
-There are few problems to do a prediction. First, the most important is that we are in 2023 and in 2020 and from2019 there is a "substantial changes were introduced as part of a new combined online survey method collecting data on both domestic overnight trips as well as domestic day trips". In my understanding this fact could imply different interpretations and results in Nights, Visits and Expenditure. 

-The second , the china's present and pandemic and lockdown follow for a worldwide economic recession and the consequences after the invasion of Ukraine make less useful a comparison between the forecasting and the reality.


---

## Visits
For the years 2018 and 2019 there were a decrease in visits and in a normal circumstances , it would logic speak in a slowly decrease or a dramatic increase like between the years 2015 and 2017. It could refereed  as 'brexit times'
```{r}
predict_visits %>% 
  select(year, breakdown_of_domestic_tourism,tourism_activity,value = value) %>% 
  filter(breakdown_of_domestic_tourism == 'Visits') %>% 
   filter(tourism_activity == 'All') %>% 
  ggplot()+
  geom_line(aes(x = year, y = value ), colour = "blue")+
  labs(
    title = "GB Total Tourism Activity Visits in Scotland between 2013 -2019",
    x = "\nYear",
    y = "millions Visits\n") +
   scale_x_continuous(breaks = 2013:2019)
```

---
##
There were a peak in 2017 in visits to tourism_activity and expenditure, after there are a decrease in total number of visits but a decrease in expenditure. That could means an increase of price of the activities, less offer?. Less tourism but more money or visitors with more/ higher purchasing power

```{r}
predict_spend %>% 
  filter(tourism_activity == 'All') %>% 
  ggplot()+
  geom_line(aes(x = year, y = value ), colour = "blue")+
  labs(
    title = "GB  Expenditure in Scotland between 2013 -2019",
    x = "\nYear",
    y = "millions Pounds\n") +
   scale_x_continuous(breaks = 2013:2019)
```


---




