---
title: "R Notebook"
output: html_notebook
---
```{r}
library(tidyverse)
library(janitor)
library(fable)
library(tsibble)
```

```{r}
regional_domestic_tourism_clean
```

```{r}
scottish_accomodation_occupancy_clean
```

```{r}
tourism_day_visits_activities_clean
```


```{r}
tourism_day_visits_demmographics_clean
```


```{r}
tourism_day_visits_location_clean
```


```{r}
tourism_day_visits_transport_clean
```





_varios_



```{r}
tourism_day_visits_demmographics %>% 
  select(date_code,units,value,breakdown_of_domestic_tourism,age,social_grade) %>% 
  group_by(date_code,age,units) %>% 
  #filter(units == 'million pounds(GBP)') %>% 
  arrange(date_code)
```

Missing where is spent the money?Need another table!!!!!!!!

```{r}
tourism_day_visits_demmographics %>% 
  select(date_code,units,value,breakdown_of_domestic_tourism,age,social_grade) %>% 
  group_by(date_code,age,breakdown_of_domestic_tourism) %>% 
  filter(breakdown_of_domestic_tourism == 'Expenditure') %>% 
  arrange(date_code)
```

```{r}
tourism_demographic_location_activities %>%    
  select(year,units,value,breakdown_of_domestic_tourism,age, tourism_activity,type_of_location_visited) %>% 
  group_by(year,age,breakdown_of_domestic_tourism) %>% 
  filter(breakdown_of_domestic_tourism == 'Expenditure') %>% 
  arrange(year,desc (value))
```
_Ejemplos_
bar_char

Problem, only X
```{r}
scottish_accomodation_occupancy_clean %>% 
  ggplot(aes( x = accommodation_type_and_occupancy))+
  geom_bar(fill = "light blue", colour = "red")
```

                    
                     _ANSWWERS_
                     
                     
Definition of a tourism activity:

Q1 Value of the tourism for Scotland
```{r}
tourism_day_visits_activities_clean %>%
  select(year,units,value,tourism_activity) %>% 
  filter(tourism_activity == 'All') %>% 
  filter(units == 'million pounds (GBP)') %>% 
  arrange(desc(value)) %>% 
  ggplot(aes( x = year, y = value))+
  geom_col(fill = "light blue", colour = "purple", position = 'dodge')+
  labs(title =  'Value of the GB tourism for Scotland', subtitle = '2013 -2019 Income', x = 'Year', y = 'million pounds' )+
  scale_x_continuous(breaks = 2013:2019)
```

Q1. Higest income for Scotland in 2019

```{r}
tourism_day_visits_activities_clean %>%
  select(year,units,value,tourism_activity) %>%
  filter(tourism_activity != 'All') %>% 
  filter(year == 2019) %>% 
  arrange(desc(year)) %>% 
   ggplot(aes( x =reorder(tourism_activity,value), y = value))+
  geom_col(fill = "light blue", #colour = "purple",
           position = 'dodge')+
  labs(title = '2019 Highest income' )+
  xlab('tourism activity' )+
  ylab('million pounds' )+
  coord_flip()
 
```


Q1 SECOND PART
_What kind of tourism activity generates the highest income for Scotland?_

TOURIST ACTIVITY highest income. There are data from 2013 CHECK THE DATA. Only inter

```{r}
tourism_day_visits_activities_clean %>%
  select(year,units,value,tourism_activity) %>% 
  arrange(desc(value))
  
```
_Filter by year_
```{r}
tourism_day_visits_activities_clean %>%
  select(year,units,value,tourism_activity) %>% 
  filter(year == 2019) %>% 
  arrange(desc(year))
```

 _Filter by year_  between 2019 -2013
```{r}
tourism_day_visits_activities %>%
  select(date_code,units,value,tourism_activity) %>% 
  filter(date_code == 2015) %>% 
   arrange(desc(value))
```



Q2 _Which kind of activity generates the most visits to sites?_

First. where go people and where they spend their money

```{r}
tourism_day_visits_location_clean %>% 
  select(year, value, type_of_location_visited, breakdown_of_domestic_tourism) %>% 
  filter(breakdown_of_domestic_tourism != 'Expenditure') %>% 
  filter(year == 2019) %>% 
   arrange(desc(value))
```

```{r}
tourism_day_visits_location_clean %>% 
  select(year, value, type_of_location_visited, breakdown_of_domestic_tourism) %>% 
  filter(breakdown_of_domestic_tourism != 'Expenditure') %>% 
  filter(type_of_location_visited != 'All areas') %>% 
  filter(year == 2019) %>% 
   arrange(desc(value)) %>% 
  ggplot(aes( x =reorder(type_of_location_visited,value), y = value))+
  geom_col(fill = "light blue", #colour = "purple",
           position = 'dodge')+
  labs(title = 'GB Visits in 2019' )+
  xlab('Location Visited' )+
  ylab('million visit' )+
  coord_flip()
  
```
 
```{r}
tourism_day_visits_location_clean %>% 
  select(year, value, type_of_location_visited, breakdown_of_domestic_tourism) %>% 
  filter(breakdown_of_domestic_tourism != 'Visits') %>% 
  filter(type_of_location_visited != 'All areas') %>% 
  filter(year == 2019) %>% 
   arrange(desc(value)) %>% 
  ggplot(aes( x =reorder(type_of_location_visited,value), y = value))+
  geom_col(fill = "light blue", #colour = "purple",
           position = 'dodge')+
  labs(title = 'GB Expenditure in 2019' )+
  xlab('Location Visited' )+
  ylab('million pounds' )+
  coord_flip()
```
 
 From 2013 to 2019
 
```{r}
tourism_day_visits_location_clean %>% 
  select(year, value, type_of_location_visited, breakdown_of_domestic_tourism) %>% 
  filter(breakdown_of_domestic_tourism != 'Expenditure') %>% 
  filter(type_of_location_visited != 'All areas') %>% 
   ggplot(aes( x = year, y = value, colour = type_of_location_visited))+
  geom_line() +
  facet_wrap(~type_of_location_visited, scales = 'free_y')+
labs(
    title = "GB Visits in Scotland between 2013 -2019",
    x = "\nyear",
    y = "millions visits\n") +
    scale_colour_brewer(guide = "none", palette = "Set2")+
   scale_x_continuous(breaks = 2013:2019)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

```{r}
tourism_day_visits_location_clean %>% 
  select(year, value, type_of_location_visited, breakdown_of_domestic_tourism) %>% 
  filter(breakdown_of_domestic_tourism != 'Visits') %>% 
  filter(type_of_location_visited != 'All areas') %>% 
   ggplot(aes( x = year, y = value, colour = type_of_location_visited))+
  geom_line() +
  facet_wrap(~type_of_location_visited, scales = 'free_y')+
labs(
    title = "GB Expenditure in Scotland between 2013 -2019",
    x = "\nyear",
    y = "Value\n") +
    scale_colour_brewer(guide = "none", palette = "Set2")+
   scale_x_continuous(breaks = 2013:2019)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

 Q2 _Which kind of activity generates the most visits to sites?_ /// SEGUNDA PARTE
 
```{r}
tourism_day_visits_location_clean
```
```{r}
tourism_day_visits_location_clean %>% 
  select(year, value, type_of_location_visited, breakdown_of_domestic_tourism) %>% 
  filter(breakdown_of_domestic_tourism != 'Visits') %>% 
  filter(year == 2014) %>% 
   arrange(desc(value))
```
 
```{r}
tourism_day_visits_location_clean %>% 
  select(year, value, type_of_location_visited, breakdown_of_domestic_tourism) %>% 
  filter(breakdown_of_domestic_tourism != 'Expenditure') %>% 
  filter(year == 2014) %>% 
   arrange(desc(value))
```

It can be observed   that for the year 2019  visits and expenditure are correlated except for the values Village/Rural countryside. In happens as well in the year 2018, 2014


Q3 _Is there a particular key demographic of visitors we should be focusing on? Who spends the most? Who visits the most?_


```{r}
tourism_day_visits_demmographics_clean
```


#  Millions Visits by age.Time range 2013-2019 More visits people under 24.

```{r}
tourism_day_visits_demmographics_clean %>% 
  filter(year == 2019) %>% 
  filter(breakdown_of_domestic_tourism =="Visits") %>% 
  filter(age != "All") %>% 
  arrange(desc(value))
```

# Millions Expenditure by visitors age. More spend people between 25-34 , 55-56 and 35-44.


```{r}
tourism_day_visits_demmographics_clean %>% 
  filter(year == 2019) %>% 
  filter(breakdown_of_domestic_tourism =='Expenditure') %>% 
  filter(age != "All") %>% 
  arrange(desc(value))
```

Age or Gender. More Female than Male 

```{r}
tourism_day_visits_demmographics_clean %>% 
  filter(year == 2019) %>% 
  filter(breakdown_of_domestic_tourism =='Expenditure') %>% 
  #filter(age != "All") %>% 
  filter(gender != "All" ) %>% 
  arrange(desc(value))
```
# Marital Status
 And much more married than not married.
```{r}
tourism_day_visits_demmographics_clean %>% 
  filter(year == 2019) %>% 
  filter(breakdown_of_domestic_tourism =='Expenditure') %>% 
  #filter(age != "All") %>% 
  #filter(gender != "All" ) %>% 
  filter(marital_status !="All") %>% 
  arrange(desc(value))
```
# Childrens? NO! very interesting! 
```{r}
tourism_day_visits_demmographics_clean %>% 
  filter(year == 2019) %>% 
  filter(breakdown_of_domestic_tourism =='Expenditure') %>% 
  #filter(age != "All") %>% 
  #filter(gender != "All" ) %>% 
  filter(children !="All") %>% 
  arrange(desc(value))
```

# Millions Expenditure by employment_status.
The gross part is, obviously, spend by employed / self-employed persons. We can questioning about the consequences about the fact that 715 millions are spend by unemployed or not working people, maybe this total amount is the reflection of students plus retired people. Segun los datos hay 998 millones que no se saben donde estan o que no han respondido

```{r}
tourism_day_visits_demmographics_clean %>% 
  select(area, year,measurement,units,value,breakdown_of_domestic_tourism,employment_status) %>% 
  filter(year == 2019) %>% 
  filter(breakdown_of_domestic_tourism =='Expenditure') %>% 
  #filter(age != "All") %>% 
  #filter(gender != "All" ) %>% 
  #filter(marital_status !="All") %>% 
  filter(employment_status != "All") %>% 
  arrange(desc(value))
```
Is important the social grade? Is ethical?Funny the most expenditure is the highest grade occupation but the second is in theory the lowest grade occupation ( less money/ less cultured person? assumption)
```{r}
tourism_day_visits_demmographics_clean %>% 
  select(area, year,measurement,units,value,breakdown_of_domestic_tourism,social_grade) %>% 
  filter(year == 2019) %>% 
  filter(breakdown_of_domestic_tourism =='Expenditure') %>% 
  filter(social_grade != "All") %>% 
  arrange(desc(value))
```
Answer. so young couples, maybe more females  with good salaries and no children


Q4 _What type of locations receive the most visits? What kinds of locations do people spend the most in?_ 
# tourism_day_visits_location_clean + tourism_day_visits_activities_clean = answer question2!!!!!!

```{r}
visit_sites_activity
```

 Sites visits by activity. Data from 2013 to 2019


```{r}
visit_sites_activity %>%
  filter(breakdown_of_domestic_tourism == 'Visits') %>% 
  filter(type_of_location_visited != 'NA') %>% 
  filter(year ==2013) %>% 
  arrange(year, tourism_activity)
```
There is a 'problem' the maths doesnt work for 2013  the 124 million visits 'All areas' is unequal to the sum of different locations. Without filter NA there are a lot of more information = millions visits lost. I show the first one by year and the first one with tourism activity.


VISITS
2019- 59million visit	  City/large town           unknown tourism_activity (1st) Note: It could be Edinburgh/ Glasgow
2019-  9	              Seaside resort or town	Day trips/excursions for other leisure purpose   tourism_activity (5th)
2018- 64	              City/large town         unknown tourism_activity (1st) Note: It could be Edinburgh/ Glasgow
2018- 38	              Small town	            	Went out for a meal  tourism_activity(2nd)
2017- 70	              City/large town         unknown tourism_activity (1st) Note: It could be Edinburgh/ Glasgow
2017- 21	              Rural countryside		    Shopping for items that you do not regularly buy  tourism_activity(3rd)
2016- 61                City/large town         unknown tourism_activity (1st) Note: It could be Edinburgh/ Glasgow
2016-  5	              Seaside - beach	        Special personal events e.g. wedding, graduation  tourism_activity(6th)
2015- 59                City/large town         unknown tourism_activity (1st) Note: It could be Edinburgh/ Glasgow
2015- 11                Village                 Visitor attraction e.g. theme park, museum, zoo  tourism_activity(4th)
2014- 59 million visit  City/large town         unknown tourism_activity (1st) Note: It could be Edinburgh/ Glasgow (commonwealth games Glasgow)
2014- 19 million visit  Rural countryside       General day out/ to explore an area  tourism_activity(3rd)
2013- 59 million visits	City/large town	         unknown tourism_activity (1st) Note: It could be Edinburgh/ Glasgow
2013- 18                Rural countryside       Night out to a bar, pub and/or club  tourism_activity(3rd)


EXPENDITURE (1st place and 2nd place)

2019- 3400 million pounds (GBP)		City/large town	    unknown tourism_activity (1st) Note: It could be Edinburgh/ Glasgow         
2019- 1456	                      Small town          unknown tourism_activity (2nd)
2018- 3111	                      City/large town     unknown tourism_activity (1st) Note: It could be Edinburgh/ Glasgow
2018- 1234	                      Small town         unknown tourism_activity (2nd)
2017- 3379	                      City/large town     unknown tourism_activity (1st) Note: It could be Edinburgh/ Glasgow
2017- 1377	                      Small town          unknown tourism_activity (2nd)
2016- 2630	                      City/large town     unknown tourism_activity (1st) Note: It could be Edinburgh/ Glasgow
2016- 1037	                      Small town          unknown tourism_activity (2nd)
2015- 2254	                      City/large town     unknown tourism_activity (1st) Note: It could be Edinburgh/ Glasgow
2015-  914	                      Small town          unknown tourism_activity (2nd)
2014- 2873 	                      City/large town     unknown tourism_activity (1st) Note: It could be Edinburgh/ Glasgow
2014- 1398	                      Small town         unknown tourism_activity (2nd)
2013- 2850	                      City/large town    unknown tourism_activity (1st) Note: It could be Edinburgh/ Glasgow
2013- 1035	                      Small town          unknown tourism_activity (2nd)


Only tourism_activity
```{r}
visit_sites_activity %>%
  filter(breakdown_of_domestic_tourism == 'Visits') %>% 
  filter(type_of_location_visited != 'NA') %>% 
  filter(tourism_activity != 'NA') %>% 
  filter(year== 2013) %>% 
  arrange( tourism_activity)
```
Total vale of All "types_of_location_visited" (124) is different to the independent sum of the each value, check what they say in the web. But I think the answer is that one person can visited multiple location. It is the same even you dont filter NA.  


Q5 _Is there a particular method of travel our visitors arrive by? Some of our locations are remote and not easily accessible by public transport, so this would be good information to have_

  In my opinion the data mix to important questions how they arrive to Scotland and how they move around Scotland.
 As we data only cover GB (England, Scotland, Wales). Which scottish airport has conections with the rest of the Island? At least, Edinburgh and Glasgow have.Travels by plane can take a taxi, car hire or tram (edinburgh) some questions have multiple answers. One visitor/visitors can use different method travel, arrive to  an airport city like Edinburgh by plane, go to accommodation by taxi,regular bus or Tram and later walk around the city.
Maybe the train is used for move between large/ medium cities  and car  for small and rural. 

```{r}
tourism_day_visits_transport_clean
```
```{r}
tourism_day_visits_transport_clean %>% 
  filter(year == 2019) %>% 
  filter(breakdown_of_domestic_tourism =='Visits') %>% 
  arrange(desc(value))
```

There are feew things interesting, 0.5 million visitis arrive by see(boat/ship/ ferry) where is cruise is boat a cruise? ship and ferry can include go to the Islands? only 0.4 take a caravan or campervan but the value of their spend is 24.2 millions of pounds 


```{r}
tourism_day_visits_transport_clean %>% 
  filter(year == 2019) %>% 
  filter(breakdown_of_domestic_tourism =='Visits') %>% 
  filter(method_of_travel != 'All') %>% 
  arrange(desc(value)) %>% 
  ggplot(aes(x =reorder(method_of_travel,value), y = value))+
  geom_col(fill = "light blue", #colour = "purple",
           position = 'dodge')+
  labs(title = 'GB Travel Visits in 2019' )+
  xlab('Method of travel' )+
  ylab('million visit' )+
  coord_flip()


```


```{r}
tourism_day_visits_transport_clean %>% 
  filter(year == 2019) %>% 
  filter(breakdown_of_domestic_tourism =='Expenditure') %>% 
   filter(method_of_travel != 'All') %>%
  arrange(desc(value)) %>% 
  ggplot(aes(x =reorder(method_of_travel,value), y = value))+
  geom_col(fill = "light blue", #colour = "purple",
           position = 'dodge')+
  labs(title = 'GB Expenses By Travel Method in 2019' )+
  xlab('Method of travel' )+
  ylab('million pounds' )+
  coord_flip()
```

En 2019 el transporte por avion solo trajo poco menos de millon y medio de visitas ( 10 puesto0) pero a cambio trajo 123 millones de  libras(7 puesto). Planes is more to arrive to any airport and later take a hired vehicle , taxi.... so its a way to arrive to scotland more than travel around the country.

How travel people and their expenditure in relation

Q6 _When looking at regional tourism, what insights can we gain? Where are our visitors from? How do they differ in the money they spend, nights they spend in Scotland, or number of visits they do?_

```{r}
regional_domestic_tourism_clean
```
Issues : the year is an average of 3 years , All GB means England, Scotland and Wales. But its only, Scotland and England in observations but not Wales and its difficult to substract  this country from 'All GB'

I am not interested!!!!!!
```{r}
regional_domestic_tourism_clean %>% 
  group_by(breakdown_of_domestic_tourism) %>% 
  count()
```
```{r}
regional_domestic_tourism_clean %>% 
  select( area ,year, value, units,region_of_residence,breakdown_of_domestic_tourism ) %>% 
  group_by(year) %>% 
  filter(region_of_residence == 'All of GB') %>% 
  filter(breakdown_of_domestic_tourism == 'Nights')
  
```

```{r}
regional_domestic_tourism_clean %>% 
  select( area ,year, value, units,region_of_residence,breakdown_of_domestic_tourism ) %>% 
  group_by(year) %>% 
  filter(region_of_residence == 'England') %>% 
  filter(breakdown_of_domestic_tourism == 'Expenditure') %>% 
  arrange(year)
```



```{r}
regional_domestic_tourism_clean %>% 
  select( area ,year, value, units,region_of_residence,breakdown_of_domestic_tourism ) %>% 
  filter(year == '2017-2019') %>% 
  filter(region_of_residence == 'All of GB') %>% 
  filter(area != 'Scotland') %>% 
  filter(breakdown_of_domestic_tourism == 'Expenditure') %>% 
  arrange(desc(value))
```

Unfortunately no works a Data viz with geom_point to many areas

```{r}
regional_domestic_tourism_clean %>% 
  select( area ,year, value, units,region_of_residence,breakdown_of_domestic_tourism ) %>% 
 #group_by(area) %>% 
  filter(year == '2017-2019') %>% 
  filter(region_of_residence == 'All of GB') %>% 
  filter(area != 'Scotland') %>% 
  filter(breakdown_of_domestic_tourism == 'Expenditure') %>% 
  arrange(desc(value)) %>% 
   ggplot(aes(x =reorder(area,value), y = value))+
  geom_col(fill = "light blue", #colour = "purple",
           position = 'dodge')+
  labs(title = 'GB Expenses By Regions during period 2017- 2019' )+
  xlab('Scottish Region' )+
  ylab('million pounds' )+
  coord_flip()
  
```
What could we deduce? it is not how to arrive, the west Hebridies ( Na h-Elleanan Siar) is over regions of the 'Central bell' it is the offer fro activities


```{r}
regional_domestic_tourism_clean %>% 
  select( area ,year, value, units,region_of_residence,breakdown_of_domestic_tourism ) %>% 
  filter(year == '2017-2019') %>% 
  filter(region_of_residence == 'All of GB') %>% 
  filter(area != 'Scotland') %>% 
  filter(breakdown_of_domestic_tourism == 'Visits') %>% 
  arrange(desc(value)) %>% 
   ggplot(aes(x =reorder(area,value), y = value))+
  geom_col(fill = "light blue", #colour = "purple",
           position = 'dodge')+
  labs(title = 'GB Visits By Regions during period 2017- 2019' )+
  xlab('Scottish Region' )+
  ylab('Thousand visits' )+
  coord_flip()
```

```{r}
regional_domestic_tourism_clean %>% 
  select( area ,year, value, units,region_of_residence,breakdown_of_domestic_tourism ) %>% 
  filter(year == '2017-2019') %>% 
  filter(region_of_residence == 'All of GB') %>% 
  filter(area != 'Scotland') %>% 
  filter(breakdown_of_domestic_tourism == 'Nights') %>% 
  arrange(desc(value)) %>% 
   ggplot(aes(x =reorder(area,value), y = value))+
  geom_col(fill = "light blue", #colour = "purple",
           position = 'dodge')+
  labs(title = 'GB Nights By Regions during period 2017- 2019' )+
  xlab('Scottish Region' )+
  ylab('Thousand Nights' )+
  coord_flip()
```
The nights are possible related to what can you do there? The offer, obviously for Highland or the big cities is more than for areas like the ' central bell' where the normal should be to stay in edinburgh/Glasgow and from there travel and back at the same day.


Q7 _What type of accommodation is most popular? Is there a difference by location?_
Viene Location of the accomodation pero no dicen de donde son los ocupantes.
The answer is that it is prefered the hotel in each type of location but it depends the offer available. The data not reflect if the accommodation was during weekday or weekend. 
```{r}
scottish_accomodation_occupancy_clean
```

```{r}
scottish_accomodation_occupancy_clean %>% 
  group_by(accommodation_type_and_occupancy) %>% 
  summarise()
```
```{r}
scottish_accomodation_occupancy_clean %>% 
  group_by(weekday_weekend) %>% 
  summarise()
```

during weekdays and weekends

```{r}
scottish_accomodation_occupancy_clean %>%
  select(area,year,value,accommodation_type_and_occupancy,location, weekday_weekend) %>% 
  filter(year == 2019) %>% 
  filter(location == 'All') %>% 
  filter(weekday_weekend == 'Weekend') %>% 
  group_by(accommodation_type_and_occupancy) %>% 
  arrange(desc(value),accommodation_type_and_occupancy)
```
```{r}
  scottish_accomodation_occupancy_clean %>%
  select(area,year,value,accommodation_type_and_occupancy,location, weekday_weekend) %>% 
  filter(year == 2019) %>% 
  filter(location == 'All') %>% 
  filter(weekday_weekend == 'Weekday') %>% 
  group_by(accommodation_type_and_occupancy) %>% 
  arrange(desc(value),accommodation_type_and_occupancy)
```


Note:/ question self-catering is rent a flat/  airB&B?
The preference of the accommodation is linked to location and its offer available.

```{r}
scottish_accomodation_occupancy_clean %>%
  select(area,year,value,accommodation_type_and_occupancy,location,weekday_weekend) %>% 
  filter(year == 2019) %>% 
  filter(location == 'Large Urban Areas') %>% 
  group_by(accommodation_type_and_occupancy) %>% 
  arrange(desc(value),accommodation_type_and_occupancy)
```
```{r}
scottish_accomodation_occupancy_clean %>%
  select(area,year,value,accommodation_type_and_occupancy,location) %>% 
  filter(year == 2019) %>% 
  filter(location == 'Accessible Small Towns') %>% 
  group_by(accommodation_type_and_occupancy) %>% 
  arrange(desc(value),accommodation_type_and_occupancy)
```
```{r}
scottish_accomodation_occupancy_clean %>%
  select(area,year,value,accommodation_type_and_occupancy,location) %>% 
  filter(year == 2019) %>% 
  filter(location == 'Other Urban Areas') %>% 
  group_by(accommodation_type_and_occupancy) %>% 
  arrange(desc(value),accommodation_type_and_occupancy)
```


```{r}
scottish_accomodation_occupancy_clean %>%
  select(area,year,value,accommodation_type_and_occupancy,location) %>% 
  filter(year == 2019) %>% 
  filter(location == 'Remote Rural') %>% 
  group_by(accommodation_type_and_occupancy) %>% 
  arrange(desc(value),accommodation_type_and_occupancy)
```


```{r}
scottish_accomodation_occupancy_clean %>%
  select(area,year,value,accommodation_type_and_occupancy,location) %>% 
  filter(year == 2019) %>% 
  filter(location == 'Accessible Rural') %>% 
  group_by(accommodation_type_and_occupancy) %>% 
  arrange(desc(value),accommodation_type_and_occupancy)
```


Q8 _How have general tourism rates changed over time?_


 _OCCUPANCY_
Change over the years, different size of the occupancy by its type
```{r}
#To avoid problems because there are too many points: group-by and summarise
scottish_accomodation_occupancy_clean %>% 
  group_by(accommodation_type_and_occupancy, year) %>% 
  summarise( average_occupancy = mean(value)) %>% 
ggplot(aes( x = year, y = average_occupancy, colour = accommodation_type_and_occupancy))+
  geom_line() +
  facet_wrap(~accommodation_type_and_occupancy, scales = 'free_y')+
labs(
    title = "GB Occupancy in Scotland between 2011 -2019",
    x = "\nYear",
    y = "Average occupancy\n") +
    scale_colour_brewer(guide = "none", palette = "Set2")+
   scale_x_continuous(breaks = 2011:2019)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


 _VISITS/LOCATIONS_
In general we see there is a tendency to a slowly fall in the visits for all GB to Scotland. This fact is more clear in 'urban' areas or where it could be more visitors.

```{r}
tourism_day_visits_location_clean %>% 
  filter(breakdown_of_domestic_tourism =='Visits') %>% 
  group_by(type_of_location_visited, year) %>% 
  summarise( average_visits = mean(value)) %>% 
ggplot(aes( x = year, y = average_visits, colour = type_of_location_visited))+
  geom_line() +
  facet_wrap(~type_of_location_visited, scales = 'free_y')+
labs(
    title = "GB Visits in Scotland between 2011 -2019",
    x = "\nYear",
    y = "Average visits\n") +
    scale_colour_brewer(guide = "none", palette = "Set2")+
   scale_x_continuous(breaks = 2011:2019)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


_DEMOGRAPHICS_
By age, each year is different, for 2019 the data show that mostly all the age groups falland the only two that grow significantly , 65 or older and 35-44 years old , are under the mark of their beat year that was 2016.

```{r}
tourism_day_visits_demmographics_clean %>% 
  select(breakdown_of_domestic_tourism, age, value,year) %>% 
  filter(age != 'All') %>% 
  filter(breakdown_of_domestic_tourism == 'Visits') %>% 
  ggplot(aes( x = year, y = value, colour = age))+
  geom_line()+
  labs(
    title = "GB Visitors Age in Scotland between 2011 -2019",
    x = "\nYear",
    y = "Average Thousand visits\n") +
   scale_colour_brewer( palette = "Set2")+
   scale_x_continuous(breaks = 2013:2019)
```
_TRANSPORT_
The car wins but b


```{r}
tourism_day_visits_transport_clean %>% 
  select(method_of_travel,breakdown_of_domestic_tourism, value,year) %>% 
  filter(method_of_travel != 'All') %>% 
  filter(breakdown_of_domestic_tourism == 'Visits') %>% 
  ggplot(aes( x = year, y = value, colour = method_of_travel))+
  geom_line()+
  labs(
    title = "GB Visitors Transport in Scotland between 2011 -2019",
    x = "\nYear",
    y = "millions visits\n") +
   scale_x_continuous(breaks = 2013:2019)
```

```{r}
tourism_day_visits_transport_clean %>% 
  select(method_of_travel,breakdown_of_domestic_tourism, value,year) %>% 
  filter(method_of_travel != 'All') %>% 
  filter(breakdown_of_domestic_tourism == 'Visits') %>% 
  ggplot(aes( x = year, y = value, colour = method_of_travel))+
  geom_line()+
   facet_wrap(~method_of_travel, scales = 'free_y')+
  labs(
    title = "GB Visitors Transport in Scotland between 2011 -2019",
    x = "\nYear",
    y = "millions visits\n") +
   scale_x_continuous(breaks = 2013:2019)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


```{r}
tourism_day_visits_transport_clean %>% 
  select(method_of_travel,breakdown_of_domestic_tourism, value,year) %>% 
  filter(method_of_travel != 'All') %>% 
  filter(breakdown_of_domestic_tourism == 'Expenditure') %>% 
  ggplot(aes( x = year, y = value, colour = method_of_travel))+
  geom_line()+
   facet_wrap(~method_of_travel, scales = 'free_y')+
  labs(
    title = "GB Visitors Transport Expenditure in Scotland between 2011 -2019",
    x = "\nYear",
    y = "millions Pounds\n") +
  # scale_colour_brewer(guide = "none", palette = "Set2")+
   scale_x_continuous(breaks = 2013:2019)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```






Q9 _Is there any way to predict spending and visits for Visit Scotland?_
Predictions with 'tourims_day_visits_location_clean.
As it was mentioned before the data covers mostly the period 2013- 2019. There are few problems to do a prediction. First, the most important is that we are in 2023 and in 2020  "substantial changes were introduced as part of a new combined online survey method collecting data on both domestic overnight trips as well as domestic day trips". In my understanding this fact could imply different interpretations and results in Nights, Visits and Expenditure. The second , the china's present and pandemic and lockdown follow for a worldwide economic recession and the consequences after the invasion of Ukraine make less useful a comparison between the forecasting and the reality.
HOWEVER, HOW SHOULD BE?   

```{r}
tourism_day_visits_demmographics_clean
```

```{r}
tourism_day_visits_demmographics_clean %>% 
  select(breakdown_of_domestic_tourism, age, value,year) %>% 
  filter(age != 'All') %>% 
  filter(breakdown_of_domestic_tourism == 'Visits') %>% 
  autoplot()
```









_Extension_
Decission Tree Age-expenditure



