---
title: "Visit Scotland. A glimpse"
author: "Juan Ignacio De Vicente"
date: "2022-12-28"
output: html_document
---

Diary. Wednesday 28/12/22. Create folders, documents, check data. Revise main questions and add notes with with more questions.
Will be necessary join all the tables?
Diary. Thursday. stop try to clean data and start create some of the code to answer the questions.
Diary. Friday. Work in question 3, join two dataset for investigate an answer.




    Dictionary
It is unclear the meaning of some  variables.

    Some reflections about the data.

In "Regional domestic tourism data" the date_code is quite unclear, is a period of 2 or 3 years from 1st January till 31st December? Also, in some case the periods take years from other periods. The data has a period-time from 2010 till 2019 that is different from other data sets. 
Try to avoid this data 


Regions means Countries inside GB ( NOT UK which include North Ireland) that means England, Scotland and Wales. However the data doesn't have any observation with Wales, why?. ecuse its incedence is too small.


Standards were change in 2019, the data is before that date.


Are the data right/ precise? Correct reading

Social grades. maybe needed for answer any question


AB	Higher & intermediate managerial, administrative, professional occupations	
C1	Supervisory, clerical & junior managerial, administrative, professional occupations	
C2	Skilled manual occupations	
DE	Semi-skilled & unskilled manual occupations, Unemployed and lowest grade occupations


Assumptions.
Percentage in accommodation_occupancy means "days per year" but is an average of what? Of the total of each type  of accomodation.

Better no compare by regions? 

The regional Data Has To Be Compare between 2013-2015 OR 2016 -2019. 

So any question relate to  regional_domestic _tourism will be checked from 2016.

Some data, when there are age  there are missing other variables , I could affect the interpretation, could mix with other data to avoid this issue?


For questions related with accommodation : "Large Urban Areas (settlements of over 125,000 people); Other Urban Areas (settlements of 10,000 to 124,999 people); Accessible Small Towns (settlements of 3,000 to 9,999 people and within 30 minutes drive of a settlement of 10,000 or more); Remote Small Towns (settlements of 3,000 to 9,999 people and with a drive time of over 30 minutes to a settlement of 10,000 or more); Accessible Rural (settlements of less than 3,000 people and within 30 minutes drive of a settlement of 10,000 or more); Remote Rural (settlements of less than 3,000 people and with a drive time of over 30 minutes to a settlement of 10,000 or more)". Also its optional and annual average, so its likely unrealistic.


Main Questions.

_What kind of tourism activity generates the highest income for Scotland?_
_Which kind of activity generates the most visits to sites?_
_Is there a particular key demographic of visitors we should be focusing on? Who spends the most? Who visits the most?_
_What type of locations receive the most visits? What kinds of locations do people spend the most in?_
_Is there a particular method of travel our visitors arrive by? Some of our locations are remote and not easily accessible by public transport, so this would be good information to have_
_When looking at regional tourism, what insights can we gain? Where are our visitors from? How do they differ in the money they spend, nights they spend in Scotland, or number of visits they do?_
_What type of accommodation is most popular? Is there a difference by location?_
_How have general tourism rates changed over time?_
_Is there any way to predict spending and visits for Visit Scotland?_





INTRODUCTION / SLIDE 1

The aim of this presentation is to show a quick glimpse about the tourist sector between the years 2011 and 2019 in Scotland.Specially the value of visits and the expenditure.

In order to conduct this premise, it had been used the the open data offer by 'Visit Scotland' that can be consult in the website of the Scottish Government : 'statistics.gov.scot'



## Data Context/ Disclaimer/ Assumptions - Slide2
 How is the date? any ethical problem? 
 Before start, it has to be some considerations.
-Some of the data used presented the variable 'region of residence', and observations are  'All GB', 'England' and 'Scotland'.  Due the fact that GB means England, Scotland and Wales,it has been used the the 'All GB' observation because - in our opinion- its the most accurate. 
- Also one visitor can realize more than one visits  and could lead to a misunderstanding / misinterpretation in the total number of visitors.
-In 2019, Visit Scotland in conjunction with Visit England and Visit Wales change the parameters for recording  domestic overnight trips and domestic day trips. It is believed that this new method can produce differents interpretations in visits and expenditure. More info. 'INSIGHT DEPARTMENT: GBTS 2021 Methodology and Quality'

- Therefore, the intention is to show a glimpse about how was the tourism  in the country in 2019 and during previous years. All before the introduction of the new method and the disruption caused by the pandemic and the lockdown restrictions during 2020,2021 and the beginning of 2022 plus the current world economic recession.  



##  Definitions-Slide3

Tourism day trip is defined as:

- Taking part in one of a pre-defined list of activities (based on international tourism definitions)

- Spending 3 or more hours out of the home on this activity

- The activity is not doing “very regularly” by the respondent

- The activity not being carried out in the place that the respondent lives or works

- The exception to this was trips to visitor attractions, live sporting events and special public events, which are all counted as tourism day trips even when in the place of residence, provided they fulfil the other three criteria.To



## Tourism in Scotland. Q1 -Slide Which tourist Activities are survey? Slide 4
The first Question should be how much money means the domestic tourist activity for Scotland.
 In this visualization we can see that from 2013 to 2019, the minimum was 2015 and means nearly 4 thousand millions pounds.
 
 
## Q1 Value of the tourism for Scotland Slide 5
```{r}
tourism_day_visits_activities_clean %>%
  select(year,units,value,tourism_activity) %>% 
  filter(tourism_activity == 'All') %>% 
  filter(units == 'million pounds (GBP)') %>% 
  arrange(desc(value)) %>% 
  ggplot(aes( x = year, y = value))+
  geom_col(fill = "light blue", colour = "purple", position = 'dodge')+
  labs(title =  'Value of the GB tourism for Scotland', subtitle = '2013 -2019 Income', x = 'Year', y = 'million pounds' )+
  scale_x_continuous(breaks = 2013:2019)

```

## Q1-Slide 6
Q1. Higest income for Scotland in 2019

```{r}
tourism_day_visits_activities_clean %>%
  select(year,units,value,tourism_activity, breakdown_of_domestic_tourism) %>%
  filter(tourism_activity != 'All') %>% 
  filter(breakdown_of_domestic_tourism =='Expenditure') %>% 
  filter(year == 2019) %>% 
  arrange(desc(year)) %>% 
   ggplot(aes( x =reorder(tourism_activity,value), y = value))+
  geom_col(fill = "light blue", #colour = "purple",
           position = 'dodge')+
  labs(title = 'Scotland Highest income 2019' )+
  xlab('tourism activity' )+
  ylab('million pounds' )+
  coord_flip()
 
```
"Went out for a meal" was the Highest Income. One thing you can do once per week 


However 
Q2 .
The number of higher number of visits for the same year is

```{r}
tourism_day_visits_activities_clean %>% 
  filter(breakdown_of_domestic_tourism != 'Expenditure') %>% 
  filter(year == 2019) %>% 
  filter(tourism_activity != 'All') %>% 
   arrange(desc(value)) %>% 
ggplot(aes( x =reorder(tourism_activity,value), y = value))+
  geom_col(fill = "light blue", #colour = "purple",
           position = 'dodge')+
  labs(title = 'GB Visits by Tourism Activity in 2019' )+
  xlab('Activity' )+
  ylab('million Visit' )+
  coord_flip()
```


##Q1 Where were these visits in 2019? Location, Slide 7

```{r}
tourism_day_visits_location_clean %>% 
  select(year, value, type_of_location_visited, breakdown_of_domestic_tourism) %>% 
  filter(breakdown_of_domestic_tourism != 'Expenditure') %>% 
  filter(type_of_location_visited != 'All areas') %>% 
  filter(year == 2019) %>% 
   arrange(desc(value)) %>% 
  ggplot(aes( x =reorder(type_of_location_visited,value), y = value))+
  geom_col(fill = "light blue", #colour = "purple",
           position = 'dodge')+
  labs(title = 'GB Visits in 2019' )+
  xlab('Location Visited' )+
  ylab('million visit' )+
  coord_flip()
  
```

```{r}
tourism_day_visits_location_clean %>% 
  select(year, value, type_of_location_visited, breakdown_of_domestic_tourism) %>% 
  filter(breakdown_of_domestic_tourism != 'Visits') %>% 
  filter(type_of_location_visited != 'All areas') %>% 
  filter(year == 2019) %>% 
   arrange(desc(value)) %>% 
  ggplot(aes( x =reorder(type_of_location_visited,value), y = value))+
  geom_col(fill = "light blue", #colour = "purple",
           position = 'dodge')+
  labs(title = 'GB Expenditure in 2019' )+
  xlab('Location Visited' )+
  ylab('million pounds' )+
  coord_flip()
```
##Slide8
 We can see the general tendency of visits individual for each type of location visited


```{r}
tourism_day_visits_location_clean %>% 
  select(year, value, type_of_location_visited, breakdown_of_domestic_tourism) %>% 
  filter(breakdown_of_domestic_tourism != 'Expenditure') %>% 
  filter(type_of_location_visited != 'All areas') %>% 
   ggplot(aes( x = year, y = value, colour = type_of_location_visited))+
  geom_line() +
  facet_wrap(~type_of_location_visited, scales = 'free_y')+
labs(
    title = "GB Visits in Scotland between 2013 -2019",
    x = "\nyear",
    y = "millions visits\n") +
    scale_colour_brewer(guide = "none", palette = "Set2")+
   scale_x_continuous(breaks = 2013:2019)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


 ## Slide9
 Althought the tendency is a decrease in visits to large cities , still is mostly the money is spend

```{r}
tourism_day_visits_location_clean %>% 
  select(year, value, type_of_location_visited, breakdown_of_domestic_tourism) %>% 
  filter(breakdown_of_domestic_tourism != 'Visits') %>% 
  filter(type_of_location_visited != 'All areas') %>% 
   ggplot(aes( x = year, y = value, colour = type_of_location_visited))+
  geom_line() +
  facet_wrap(~type_of_location_visited, scales = 'free_y')+
labs(
    title = "GB Expenditure in Scotland between 2013 -2019",
    x = "\nyear",
    y = "Value\n") +
    scale_colour_brewer(guide = "none", palette = "Set2")+
   scale_x_continuous(breaks = 2013:2019)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
this visualization see the evolution for the period 2013 - 2019 the visits in city/ large town has fallen but the expenditure there has increase in the last year. the Rural countryside shows the opposite the expenditure has decrease but  the visits has increase from 2018.

It can be observed   that for the year 2019  visits and expenditure are correlated except for the values Village/Rural countryside. In happens as well in the year 2018, 2014

#Q1Slide10
 How was from 2013 to 2019. Where they expend the money
 
```{r}
tourism_day_visits_activities_clean %>% 
  filter(breakdown_of_domestic_tourism != 'Expenditure') %>% 
  filter(tourism_activity != 'All') %>% 
   arrange(desc(value)) %>% 
ggplot(aes( x = year, y = value, fill = tourism_activity, label = value))+
  geom_bar(stat = 'identity')+
  geom_text(size = 3, position = position_stack(vjust = 0.5))+
labs(
    title = "GB Visits by Tourism Activity in Scotland  2013 -2019",
    x = "\nyear",
    y = "Millions visits\n") +
   scale_x_continuous(breaks = 2013:2019)+
  theme_update(plot.title = element_text(hjust = 0.445))
```

## Demographics Slide. 11

This is general evolution in the tendency of visiting by age

There is not a general tendency each group of age had a prefered year  in visit scotland

 Millions Visits by age.Time range 2013-2019 More visits people under 24.

```{r}
tourism_day_visits_demmographics_clean %>% 
  filter(breakdown_of_domestic_tourism =="Visits") %>% 
  filter(age != "All") %>% 
  arrange(desc(value)) %>% 
ggplot(aes( x = year, y = value, colour = age))+
  geom_line() +
  facet_wrap(~age, scales = 'free_y')+
labs(
    title = "GB Visits in Scotland between 2013 -2019",
    x = "\nyear",
    y = "millions visits\n") +
    scale_colour_brewer(guide = "none", palette = "Set2")+
   scale_x_continuous(breaks = 2013:2019)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## For the year 2019

```{r}
tourism_day_visits_demmographics_clean %>% 
  filter(year == 2019) %>% 
  filter(breakdown_of_domestic_tourism =="Visits") %>% 
  filter(age != "All") %>% 
  arrange(desc(value)) %>% 
ggplot(aes( x = age, y = value,fill = 'light blue'))+
     geom_col(fill = "light blue",
           position = 'dodge')+
labs(
    title = "GB Visits in Scotland in 2019",
    x = "\nAge",
    y = "millions visits\n") +
  coord_flip()+
  theme_update(plot.title = element_text(hjust = 0.5))
```

 Millions Expenditure by visitors age. More spend people between 25-34 , 55-56 and 35-44.

```{r}
tourism_day_visits_demmographics_clean %>% 
  filter(year == 2019) %>% 
  filter(breakdown_of_domestic_tourism =='Expenditure') %>% 
  filter(age != "All") %>% 
  arrange(desc(value)) %>% 
  ggplot(aes( x = age, y = value))+
  geom_col(fill = "light blue")+
labs(
    title = "GB Expenditure by Age in Scotland 2019",
    x = "\nAge",
    y = "millions Pounds\n") +
    scale_colour_brewer(guide = "none", palette = "Set2")+
  coord_flip()
```



##Last slide Total by years
Years- Age-Millions Visits

```{r}
tourism_day_visits_demmographics_clean %>% 
  filter(breakdown_of_domestic_tourism =="Visits") %>% 
  filter(age != "All") %>% 
  arrange(desc(value)) %>% 
ggplot(aes( x = year, y = value, fill = age, label = value))+
  geom_bar(stat = 'identity')+
  geom_text(size = 3, position = position_stack(vjust = 0.5))+
labs(
    title = "GB Visits by Age in Scotland between 2013 -2019",
    x = "\nyear",
    y = "Millions visits\n") +
   scale_x_continuous(breaks = 2013:2019)
```
Millions of Pounds by year

```{r}
tourism_day_visits_demmographics_clean %>% 
  filter(breakdown_of_domestic_tourism =="Expenditure") %>% 
  filter(age != "All") %>% 
  arrange(desc(value)) %>% 
ggplot(aes( x = year, y = value, fill = age, label = value))+
  geom_bar(stat = 'identity')+
  geom_text(size = 3, position = position_stack(vjust = 0.5))+
labs(
    title = "GB Expenditure by Age in Scotland between 2013 -2019",
    x = "\nyear",
    y = "Millions expenditure\n") +
   scale_x_continuous(breaks = 2013:2019)
```


## Gender. More Female than Male in 2019

```{r}
tourism_day_visits_demmographics_clean %>% 
  filter(year == 2019) %>% 
  filter(breakdown_of_domestic_tourism =='Expenditure') %>% 
  filter(gender != "All") %>% 
  filter(gender != "All" ) %>% 
  arrange(desc(value)) %>% 
  ggplot(aes( x = gender, y = value ))+
  geom_col(fill = "light blue")+
labs(
    title = "GB Expenditure by Gender in Scotland 2019",
    x = "\nAge",
    y = "millions Pounds\n") +
    scale_colour_brewer(guide = "none", palette = "Set2")+
  theme_update(plot.title = element_text(hjust = 1))
```
And we can appreciate that is a normal tendency where female expend more money than male

```{r}
tourism_day_visits_demmographics_clean %>% 
  #filter(year == 2019) %>% 
  filter(breakdown_of_domestic_tourism =='Expenditure') %>% 
  filter(gender != "All") %>% 
  filter(gender != "All" ) %>% 
  arrange(desc(value)) %>% 
  ggplot(aes( x = year, y = value ))+
  geom_point(aes(colour = gender, shape = gender),size = 4)+
labs(
    title = "GB Expenditure by Gender in Scotland 2019",
    x = "\nyear",
    y = "millions Pounds\n") +
    #(guide = "none", palette = "Set2")+
    scale_x_continuous(breaks = 2013:2019)+
  theme_update(plot.title = element_text(hjust = 1))
```

## Marital Status
 And much more married than not married.
```{r}
tourism_day_visits_demmographics_clean %>% 
  filter(year == 2019) %>% 
  filter(breakdown_of_domestic_tourism =='Expenditure') %>% 
  filter(marital_status !="All") %>% 
  arrange(desc(value)) %>% 
  ggplot(aes( x = marital_status, y = value ))+
  geom_col(fill = "light blue")+
labs(
    title = "GB Expenditure by Gender in Scotland 2019",
    x = "\nTaken",
    y = "millions Pounds\n") +
    scale_colour_brewer(guide = "none", palette = "Set2")
```
_answer_ More married than no married
```{r}
tourism_day_visits_demmographics_clean %>% 
 # filter(year == 2019) %>% 
  filter(breakdown_of_domestic_tourism =='Expenditure') %>% 
  filter(marital_status !="All") %>% 
  arrange(desc(value)) %>% 
  ggplot(aes( x = year, y = value ))+
  geom_point(aes(colour = marital_status, shape = marital_status),size = 4)+
labs(
    title = "GB Expenditure by marital_status in Scotland 2019",
    x = "\nyear",
    y = "millions Pounds\n") +
    #scale_colour_brewer(guide = "none", palette = "Set2")+
    scale_x_continuous(breaks = 2013:2019)
```

## Childrens? NO! Thanks very interesting! 
```{r}
tourism_day_visits_demmographics_clean %>% 
  filter(year == 2019) %>% 
  filter(breakdown_of_domestic_tourism =='Expenditure') %>% 
  filter(children !="All") %>% 
  arrange(desc(value)) %>% 
  ggplot(aes( x = children, y = value ))+
  geom_col(fill = "light blue")+
labs(
    title = "GB Expenditure with Children in Scotland 2019",
    x = "\nChildren",
    y = "millions Pounds\n") +
    scale_colour_brewer(guide = "none", palette = "Set2")
```

## Millions Expenditure by employment_status.
The next two plots show something obvious,for 2019 is obvious that the weitgh of spend is in the working group, but the other 2 groups means 500 millions of pounds, is a lot money?
The gross part is, obviously, spend by employed / self-employed persons. We can questioning about the consequences about the fact that 715 millions are spend by unemployed or not working people, maybe this total amount is the reflection of students plus retired people.


```{r}
tourism_day_visits_demmographics_clean %>% 
  select(area, year,measurement,units,value,breakdown_of_domestic_tourism,employment_status) %>% 
  filter(year == 2019) %>% 
  filter(breakdown_of_domestic_tourism =='Expenditure') %>% 
  filter(employment_status != "All") %>% 
  arrange(desc(value)) %>% 
  ggplot(aes( x = employment_status, y = value ))+
  geom_col(fill = "light blue")+
labs(
    title = "GB Expenditure By employment_status in Scotland 2019",
    x = "\n Employment Status",
    y = "millions Pounds\n") +
    scale_colour_brewer(guide = "none", palette = "Set2")+
  theme_update(plot.title = element_text(hjust = 0.5))
```
 

```{r}
tourism_day_visits_demmographics_clean %>% 
  select(area, year,measurement,units,value,breakdown_of_domestic_tourism,employment_status) %>% 
  filter(breakdown_of_domestic_tourism =='Expenditure') %>% 
  filter(employment_status != "All") %>% 
  arrange(desc(value)) %>% 
  ggplot(aes( x = year, y = value ))+
  geom_point(aes(colour = employment_status, shape = employment_status),size = 4)+
  labs(
    title = "GB Expenditure By Employment Status in Scotland 2019",
    x = "\n Employment Status",
    y = "millions Pounds\n") +
    scale_x_continuous(breaks = 2013:2019)+
  theme_update(plot.title = element_text(hjust = 1))
```

## SocialGrade

Is important the social grade? Is ethical?Funny the most expenditure is the highest grade occupation but the second is in theory the lowest grade occupation ( less money/ less cultured person? assumption)

```{r}
tourism_day_visits_demmographics_clean %>% 
  select(area, year,measurement,units,value,breakdown_of_domestic_tourism,social_grade) %>% 
  filter(year == 2019) %>% 
  filter(breakdown_of_domestic_tourism =='Expenditure') %>% 
  filter(social_grade != "All") %>% 
  arrange(desc(value)) %>% 
 ggplot(aes( x = social_grade, y = value ))+
  geom_col(fill = "light blue")+
labs(
    title = "GB Expenditure By Social Grade in Scotland 2019",
    x = "\n Social Grade",
    y = "millions Pounds\n") +
    scale_colour_brewer(guide = "none", palette = "Set2")+
   theme_update(plot.title = element_text(hjust = -1))
```
## 
In Conclusion.
 The data point out that the profile person that spend more money  is a young / middle- age female married - maybe recently- without children with employ 


```{r}
tourism_day_visits_demmographics_clean %>% 
  select(area, year,measurement,units,value,breakdown_of_domestic_tourism,social_grade) %>% 
  filter(breakdown_of_domestic_tourism =='Expenditure') %>% 
  filter(social_grade != "All") %>% 
  arrange(desc(value)) %>% 
 ggplot(aes( x = year, y = value ))+
   geom_point(aes(colour = social_grade, shape = social_grade),size = 4)+
  labs(
    title = "GB Expenditure By Social Grade in Scotland period 2013 - 2019",
    x = "\n Social Grade",
    y = "millions Pounds\n") +
    scale_x_continuous(breaks = 2013:2019)
```

The obvious for social grade but not the last year. Is it ethical? 'help' people to spend money

## Transport means where to go, free to travel....

```{r}
tourism_day_visits_transport_clean %>% 
  filter(year == 2019) %>% 
  filter(breakdown_of_domestic_tourism =='Visits') %>% 
  filter(method_of_travel != 'All') %>% 
  arrange(desc(value)) %>% 
  ggplot(aes(x =reorder(method_of_travel,value), y = value))+
  geom_col(fill = "light blue", #colour = "purple",
           position = 'dodge')+
  labs(title = 'GB Travel Visits in 2019' )+
  xlab('Method of travel' )+
  ylab('million visit' )+
  coord_flip()
```
```{r}
tourism_day_visits_transport_clean %>% 
  filter(year == 2019) %>% 
  filter(breakdown_of_domestic_tourism =='Expenditure') %>% 
   filter(method_of_travel != 'All') %>%
  arrange(desc(value)) %>% 
  ggplot(aes(x =reorder(method_of_travel,value), y = value))+
  geom_col(fill = "light blue", #colour = "purple",
           position = 'dodge')+
  labs(title = 'GB Expenses By Travel Method in 2019' )+
  xlab('Method of travel' )+
  ylab('million pounds' )+
  coord_flip()
```
En 2019 el transporte por avion solo trajo poco menos de millon y medio de visitas ( 10 puesto) pero a cambio trajo 123 millones de  libras(7 puesto). Planes is more to arrive to any airport and later take a hired vehicle , taxi.... so its a way to arrive to scotland more than travel around the country.

##Where goews the people?
```{r}
regional_domestic_tourism_clean %>% 
  select( area ,year, value, units,region_of_residence,breakdown_of_domestic_tourism ) %>% 

  filter(year == '2017-2019') %>% 
  filter(region_of_residence == 'All of GB') %>% 
  filter(area != 'Scotland') %>% 
  filter(breakdown_of_domestic_tourism == 'Expenditure') %>% 
  arrange(desc(value)) %>% 
   ggplot(aes(x =reorder(area,value), y = value))+
  geom_col(fill = "light blue", #colour = "purple",
           position = 'dodge')+
  labs(title = 'GB Expenses By Regions during period 2017- 2019' )+
  xlab('Scottish Region' )+
  ylab('million pounds' )+
  coord_flip()
```


 What could we deduce? it is not how to arrive, the Western Islands ( Na h-Elleanan Siar) is over regions of the 'Central bell' it is the offer fro activities
 
 
```{r}
regional_domestic_tourism_clean %>% 
  select( area ,year, value, units,region_of_residence,breakdown_of_domestic_tourism ) %>% 
  filter(year == '2017-2019') %>% 
  filter(region_of_residence == 'All of GB') %>% 
  filter(area != 'Scotland') %>% 
  filter(breakdown_of_domestic_tourism == 'Visits') %>% 
  arrange(desc(value)) %>% 
   ggplot(aes(x =reorder(area,value), y = value))+
  geom_col(fill = "light blue", #colour = "purple",
           position = 'dodge')+
  labs(title = 'GB Visits By Regions during period 2017- 2019' )+
  xlab('Scottish Region' )+
  ylab('Thousand visits' )+
  coord_flip()
```
 
```{r}
regional_domestic_tourism_clean %>% 
  select( area ,year, value, units,region_of_residence,breakdown_of_domestic_tourism ) %>% 
  filter(year == '2017-2019') %>% 
  filter(region_of_residence == 'All of GB') %>% 
  filter(area != 'Scotland') %>% 
  filter(breakdown_of_domestic_tourism == 'Nights') %>% 
  arrange(desc(value)) %>% 
   ggplot(aes(x =reorder(area,value), y = value))+
  geom_col(fill = "light blue", #colour = "purple",
           position = 'dodge')+
  labs(title = 'GB Nights By Regions during period 2017- 2019' )+
  xlab('Scottish Region' )+
  ylab('Thousand Nights' )+
  coord_flip()
```
 
 ## Accommodation
 
 Hotels difference between  Rooms and Bed occupancy. Rooms for weekday and beds during weekend. Whats the meaning? Working occupancy plus leisure, a room can have a double bed occupy by one person, 
```{r}
scottish_accomodation_occupancy_clean %>%
  select(area,year,value,accommodation_type_and_occupancy,location, weekday_weekend) %>% 
  filter(year == 2019) %>% 
  filter(location == 'All') %>% 
  filter(weekday_weekend != 'All') %>% 
  group_by(accommodation_type_and_occupancy) %>% 
  arrange(desc(value),accommodation_type_and_occupancy) %>% 
  ggplot(aes(fill= weekday_weekend, y=value, x=accommodation_type_and_occupancy)) + 
    geom_bar(position="dodge", stat="identity")+
 labs(
    title ="Occupancy by Accomodation Type in Scotland  in 2019",
    x = "\n Accomodation Type",
    y = "Percentage Over Total Occupancy\n") +
   coord_flip()+
  theme_update(plot.title = element_text(hjust = 1))
```

Cheap travels for long weekends.
Note: difference Room and Bed occupancy, no clear but I  understand that Room means the number of occupants per room but Bed  means the number of occupants in a room per size bed = 1 single bed and 1 double bed  means 3 max occupants

Group barchart by  total occupation period time

```{r}
scottish_accomodation_occupancy_clean %>%
  select(area,year,value,accommodation_type_and_occupancy,location, weekday_weekend) %>% 
  filter(location == 'All') %>% 
  filter(weekday_weekend != 'All') %>% 
  group_by(accommodation_type_and_occupancy) %>% 
  arrange(desc(value),accommodation_type_and_occupancy) %>% 
  ggplot(aes(fill= weekday_weekend, y=value, x=year)) + 
    geom_bar(position="dodge", stat="identity")+
 labs(
    title = " Total Occupancy  in Scotland period 2011- 2019",
    x = "\n Accomodation Type",
    y = "Percentage Over Total Occupancy\n") +
   scale_x_continuous(breaks = 2011:2019)+
  theme(axis.text.x = element_text(angle = 25, hjust = 1))
```
 
## Occupancy rates

```{r}
#To avoid problems because there are too many points: group-by and summarise
scottish_accomodation_occupancy_clean %>% 
  group_by(accommodation_type_and_occupancy, year) %>% 
  summarise( average_occupancy = mean(value)) %>% 
ggplot(aes( x = year, y = average_occupancy, colour = accommodation_type_and_occupancy))+
  geom_line() +
  facet_wrap(~accommodation_type_and_occupancy, scales = 'free_y')+
labs(
    title = "GB Occupancy in Scotland between 2011 -2019",
    x = "\nYear",
    y = "Average occupancy\n") +
    scale_colour_brewer(guide = "none", palette = "Set2")+
   scale_x_continuous(breaks = 2011:2019)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

_VISITS/LOCATIONS_
In general we see there is a tendency to a slowly fall in the visits for all GB to Scotland. This fact is more clear in 'urban' areas or where it could be more visitors.
```{r}
tourism_day_visits_location_clean %>% 
  filter(breakdown_of_domestic_tourism =='Visits') %>% 
  group_by(type_of_location_visited, year) %>% 
  summarise( average_visits = mean(value)) %>% 
ggplot(aes( x = year, y = average_visits, colour = type_of_location_visited))+
  geom_line() +
  facet_wrap(~type_of_location_visited, scales = 'free_y')+
labs(
    title = "GB Visits in Scotland between 2011 -2019",
    x = "\nYear",
    y = "Average visits\n") +
    scale_colour_brewer(guide = "none", palette = "Set2")+
   scale_x_continuous(breaks = 2011:2019)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

_DEMOGRAPHICS_
By age, each year is different, for 2019 the data show that mostly all the age groups falland the only two that grow significantly , 65 or older and 35-44 years old , are under the mark of their beat year that was 2016.

```{r}
tourism_day_visits_demmographics_clean %>% 
  select(breakdown_of_domestic_tourism, age, value,year) %>% 
  filter(age != 'All') %>% 
  filter(breakdown_of_domestic_tourism == 'Visits') %>% 
  ggplot(aes( x = year, y = value, colour = age))+
  geom_line()+
  labs(
    title = "GB Visitors Age in Scotland between 2011 -2019",
    x = "\nYear",
    y = "Average Thousand visits\n") +
   scale_colour_brewer( palette = "Set2")+
   scale_x_continuous(breaks = 2013:2019)
```
_TRANSPORT_
The car wins but b


```{r}
tourism_day_visits_transport_clean %>% 
  select(method_of_travel,breakdown_of_domestic_tourism, value,year) %>% 
  filter(method_of_travel != 'All') %>% 
  filter(breakdown_of_domestic_tourism == 'Visits') %>% 
  ggplot(aes( x = year, y = value, colour = method_of_travel))+
  geom_line()+
  labs(
    title = "GB Visitors Transport in Scotland between 2011 -2019",
    x = "\nYear",
    y = "millions visits\n") +
   scale_x_continuous(breaks = 2013:2019)
```
Visits

```{r}
tourism_day_visits_transport_clean %>% 
  select(method_of_travel,breakdown_of_domestic_tourism, value,year) %>% 
  filter(method_of_travel != 'All') %>% 
  filter(breakdown_of_domestic_tourism == 'Visits') %>% 
  ggplot(aes( x = year, y = value, colour = method_of_travel))+
  geom_line()+
   facet_wrap(~method_of_travel, scales = 'free_y')+
  labs(
    title = "GB Visitors Transport in Scotland between 2011 -2019",
    x = "\nYear",
    y = "millions visits\n") +
   scale_x_continuous(breaks = 2013:2019)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
Expenditure

```{r}
tourism_day_visits_transport_clean %>% 
  select(method_of_travel,breakdown_of_domestic_tourism, value,year) %>% 
  filter(method_of_travel != 'All') %>% 
  filter(breakdown_of_domestic_tourism == 'Expenditure') %>% 
  ggplot(aes( x = year, y = value, colour = method_of_travel))+
  geom_line()+
   facet_wrap(~method_of_travel, scales = 'free_y')+
  labs(
    title = "GB Visitors Transport Expenditure in Scotland between 2011 -2019",
    x = "\nYear",
    y = "millions Pounds\n") +
  # scale_colour_brewer(guide = "none", palette = "Set2")+
   scale_x_continuous(breaks = 2013:2019)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


Expenditure/travel method

```{r}
tourism_day_visits_transport_clean %>% 
  select(method_of_travel,breakdown_of_domestic_tourism, value,year) %>% 
  filter(method_of_travel != 'All') %>% 
  filter(breakdown_of_domestic_tourism == 'Expenditure') %>% 
  ggplot(aes( x = year, y = value, fill = method_of_travel, label = value))+
  geom_bar(stat = 'identity')+
  geom_text(size = 3, position = position_stack(vjust = 0.5))+
  labs(
    title = "GB Visitors Transport Expenditure in Scotland between 2011 -2019",
    x = "\nYear",
    y = "millions Pounds\n") +
   scale_x_continuous(breaks = 2013:2019)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

##Q9 Predict visits

As it was mentioned before the data covers mostly the period 2013- 2019. There are few problems to do a prediction. First, the most important is that we are in 2023 and in 2020 and from2019 there is a "substantial changes were introduced as part of a new combined online survey method collecting data on both domestic overnight trips as well as domestic day trips". In my understanding this fact could imply different interpretations and results in Nights, Visits and Expenditure. The second , the china's present and pandemic and lockdown follow for a worldwide economic recession and the consequences after the invasion of Ukraine make less useful a comparison between the forecasting and the reality.

##

```{r}
predict_visits %>% 
  select(year, breakdown_of_domestic_tourism,tourism_activity,value = value) %>% 
  filter(breakdown_of_domestic_tourism == 'Visits') %>% 
   filter(tourism_activity == 'All') %>% 
  ggplot()+
  geom_line(aes(x = year, y = value ), colour = "blue")+
  labs(
    title = "GB Total Tourism Activity Visits in Scotland between 2013 -2019",
    x = "\nYear",
    y = "millions Visits\n") +
   scale_x_continuous(breaks = 2013:2019)
```
here were a peak in 2017 in visits to tourism_activity and expenditure, after there are a decrease in total number of visits but a decrease in expenditure. That could means an increase of price of the activities, less offer?. Less tourism but more money or visitors with more/ higher purchasing power

```{r}
predict_spend %>% 
  filter(tourism_activity == 'All') %>% 
  ggplot()+
  geom_line(aes(x = year, y = value ), colour = "blue")+
  labs(
    title = "GB  Expenditure in Scotland between 2013 -2019",
    x = "\nYear",
    y = "millions Pounds\n") +
   scale_x_continuous(breaks = 2013:2019)
```














_Recommendations_

-Improve the survey and join data so it can be possible to show/ investigate which activity is more visit and therefore more suitable for each group age/status..for groups of people like age or families( children).
Understand the importance of tourism in the general economy, not index more in pounds. the data only reflect the domestic visitor but not the international.

-There are no enough information to combine 'tourism activity' and 'type of location visited'.

-Issues : the year is an average of 3 years , All GB means England, Scotland and Wales. But its only, Scotland and England in observations but not Wales and its difficult to substract  this country from 'All GB' has to improve the Wales survey

-Improve the International visits/ Expenditure

- You shouldn't say that " Visit Scotland markets Scotland to all parts of the world to attract visitors" when your data provided is only partial Great Britain -Dayta from Wales is not specify- even not all UK.

So looking for a local tourism. tourism as soft power inside the Isle? In my opi nion this Data can no reflect properly  the importance of Tourism in Scottish economic. Also, because is missing the data for international tourism , not reflect the international tourist attraction of the country by its own and inside of UK and the ' soft power' imply.   
- Idea : Perhaps need division by Scotland's regions, sites. We should have data from visitors outside of GB in order to have a better understanding of the visitor and improve their experience and compare with inside of GB and see the weight of each group.